Open-Set Domain Adaptation through Self-Supervision

### 2022-02-13 paper/main.tex
minor fixes 2
minor fixes 3

\subsection{Ablation Study}
\label{sec:ablation_study}
Image \ref{fig:hyperparams} summarizes the parameter optimization process where a sequential approach is followed.
For each configuration one hyper-parameter is optimized at a time,
following the order
$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$ and picking the parameter giving the highest HOS.
Models not using center loss just skip the $\lambda_1$ optimization.
Ablation study were run on two domain shifts, 
Art $\to$ Clipart and Clipart $\to$ Product.
In appendix \ref{sec:tables} tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report all the steps followed for each configuration.
This information is also summarized in figure \ref{fig:hyperparams}.
We can notice that most of the optimal parameters are shared between configurations,
an exception being the normality score $\mathcal{\tilde N}$ on a single-headed configuration.
This is due to the fact that having to use only one head for all classes it is better to be very confident about classyfing a sample as known.
Smaller $\alpha_1$ and $\alpha_2$ values are preferred as they avoid overfitting the rotation classifiers as the object classifiers take a longer time to converge.
As center loss contributions are directly summed to the rotation classifier loss term while being much bigger, 
much smaller values need to be used for a correct model convergence.

\section{Future Work}
\label{sec:future_work}

>>>>

\subsection{Ablation Study}
\label{sec:ablation_study}
Image \ref{fig:hyperparams} summarizes the parameter optimization process where a sequential approach is followed.
For each configuration one hyper-parameter is optimized at a time,
following the order
$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$ and picking the parameter giving the highest HOS.
Models not using center loss just skip the $\lambda_1$ optimization.
Ablation study were run and averaged on two domain shifts, 
Art $\to$ Clipart and Product $\to$ Clipart.
In appendix \ref{sec:tables} tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report all the steps followed for each configuration.
This information is also summarized in figure \ref{fig:hyperparams}.
We can notice that most of the optimal parameters are shared between configurations,
an exception being the normality score $\mathcal{\tilde N}$ on a single-headed configuration.
This is due to the fact that having to use only one head for all classes it is better to be very confident about classifying a sample as known.
Smaller $\alpha_1$ and $\alpha_2$ values are preferred as they avoid overfitting the rotation classifiers as the object classifiers take a longer time to converge.
As center loss contributions are directly summed to the rotation classifier loss term while being much bigger, 
much smaller values need to be used for a correct model convergence.

\section{Future Work and conclusions}
\label{sec:future_work}
